Fetching Reprint Author information from the Web of Science

### 2019-10-11 analysis/003_kb_fetch_ca.Rmd
re-render rp dataset including updated crossref  journal info

```{r}
cr_journals <- readr::read_csv("../data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_country <- readr::read_csv("../data/rp_data_14_18.csv")
issn_l <- readr::read_tsv("../data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_country %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(`ISSN-L`= "issn_l")) %>%
  select(-issn) %>%
  distinct()
```

@@

```{r}
require(writexl)
rp_df <- readr::read_csv("../data/rp_jn_14_18.csv")
tmp <- map(2014:2018, function(x) {
  rp_df %>% 
    filter(publication_year == x)
  }
)
# names
names(tmp) <- paste0("pubyear_", 2014:2018)
write_xlsx(tmp, "../data/rp_14_18.xlsx")
```

>>>>

```{r}
cr_journals <- readr::read_csv("../data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_country <- readr::read_csv("../data/rp_data_14_18.csv")
issn_l <- readr::read_tsv("../data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_country %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(ISSN = "issn")) %>%
  distinct()
```

@@

```{r}
require(writexl)
rp_df <- readr::read_csv("../data/rp_jn_14_18.csv")
tmp <- map(2014:2018, function(x) {
  rp_df %>% 
    filter(publication_year == x)
  }
)
# names
names(tmp) <- paste0("pubyear_", 2014:2018)
write_xlsx(tmp, "../data/rp_jn_14_18.xlsx")
```
